Arrows for Parallel Computations

### 2017-11-28 paper/content/bestAndWorstBenchmarks.tex
fixed tables again

\renewcommand{\multirow}[3]{#3}
\newcommand{\meanOverhead}{
\begin{table}
\caption{Best and worst benchmark results on shared memory multiprocessors.}
\begin{tabular}{l c S S}
\toprule
	\multirow{4}{c}{\sudokutest 1000}    &	 
    {backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \midrule
    \multirow{4}{c}{\sudokutest 16000}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-16000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \midrule
    \multirow{4}{c}{\rmtest 11213 32}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \midrule
    \multirow{4}{c}{\rmtest 11213 64}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \bottomrule
    \end{tabular}
    \label{tab:overhead-smp}
\end{table}
\begin{table}
\caption{Best and worst benchmark results on a distributed memory grid.}
\begin{tabular}{l c S S}
\toprule
	\multirow{2}{c}{\torustest 4096}    &	 
    {backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
		\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \midrule
    \multirow{2}{c}{\rmtest 44497 256}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
        \midrule
    \multirow{2}{c}{\jacobitest 3217}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-3217.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \midrule
    \multirow{2}{c}{\jacobitest 4253}    &	 
	{backend}             & {mean overhead} & {max.\ normalised stdDev} \\ \midrule
    \csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-4253.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
    \bottomrule
    \end{tabular}
    \label{tab:overhead-grid}
\end{table}
}

@@

\newcommand{\meanOverheadOLD}{
\begin{table}[]
\centering
\label{tab:meanOverhead}
\captionsetup[subtable]{justification=centering}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest 1000}\label{sudokuMeanFactor-1000}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-16000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\sudokutest 16000}\label{sudokuMeanFactor-16000}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\caption{\rmtest 11213 32}\label{sm-rmMeanFactor-11213-32}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest 11213 64}\label{sm-rmMeanFactor-11213-64}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\caption{\torustest (dist) 4096}\label{torusMeanFactor-4096}
\end{subtable}
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\rmtest (dist) 44497 256}\label{dist-rmMeanFactor-44497}
\end{subtable}
\newline
\vspace*{0.5 cm}
\newline
\begin{subtable}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-4253.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \caption{\jacobitest (dist) 4253}\label{jacobiMeanFactor-4253}
\end{subtable}
\caption{Overhead in the benchmarks}
\end{table}
}

>>>>

@@

\newcommand{\meanOverheadTEST}{
\begin{table}[]
\centering
\caption{Overhead in the benchmarks}
\label{tab:meanOverhead}
\captionsetup[subtable]{justification=centering}
\subfloat[\sudokutest 1000]{
	\begin{minipage}[t]{\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{3cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{Benchmark} & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \toprule
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \benchmark \params & \meanOverhead & \maxStdDevForOverhead \\}
		\midrule
	\end{tabular}
	\endgroup
	\label{sudokuMeanFactor-1000}
	\end{minipage}
}
\caption{Overhead in the benchmarks}
\end{table}
}

\newcommand{\meanOverhead}{
\begin{table}[]
\centering
\caption{Overhead in the benchmarks}
\label{tab:meanOverhead}
\captionsetup[subtable]{justification=centering}
\subfloat[\sudokutest 1000]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-1000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{sudokuMeanFactor-1000}
	\end{minipage}
}
\subfloat[\sudokutest 16000]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sudoku-sm/bestAndWorstSudoku-16000.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{sudokuMeanFactor-16000}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\rmtest 11213 32]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-32.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{sm-rmMeanFactor-11213-32}
	\end{minipage}
}
\subfloat[\rmtest 11213 64]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/sm-rm/bestAndWorstRMSM-11213-64.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{sm-rmMeanFactor-11213-64}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\torustest (dist) 4096]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-torus/bestAndWorstTorus-4096.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
	\label{torusMeanFactor-4096}
	\end{minipage}
}
\subfloat[\rmtest (dist) 44497 256]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-rm/bestAndWorstRM-44497-256.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{dist-rmMeanFactor-44497}
	\end{minipage}
}
\newline
\vspace*{0.5 cm}
\newline
\subfloat[\jacobitest (dist) 3217]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-3217.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{jacobiMeanFactor-3217}
	\end{minipage}
}
\subfloat[\jacobitest (dist) 4253]{
	\begin{minipage}[t]{.49\linewidth}%
    \centering%
    \begingroup\catcode`"=9
	\begin{tabular}{C{2cm} C{1.7cm} C{2.3cm}}
		\thead{vs.}             & \thead{mean \\ overhead} & \thead{maximum \\ normalized \\ stdDev} \\ \hline
		\csvreader[head to column names]{benchmarks/distributed-jacobi/bestAndWorstJacobi-4253.csv}{}{\vs & \meanOverhead & \maxStdDevForOverhead \\}
	\end{tabular}
	\endgroup
    \label{jacobiMeanFactor-4253}
	\end{minipage}
}
\end{table}
}
